---
title: "Setting up an RStudio Project"
author: "Parmutia Makui"
date: 2016-10-20
categories: ["R"]
tags: ["rmarkdown", "tidyverse", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r Load libraries}

library(foreign)
suppressPackageStartupMessages(library(dplyr))

```


# Setting up an R Studio Project
## Why use R Studio Project?

- It helps in organizing work very well
- Enables better efficiency

## Creating Projects

- Open RStudio
- **Option I:** On the top left corner you will see a down-facing arrow with 
  **New project**
- **Option II:** From the menu options, click on **File** then **New Project..**  
- Use of either options should give you the New Project window shown below:

<!-- \begin{frame} -->
<!-- \frametitle{New Project Window} -->
<!-- \begin{figure} -->
<!-- \includegraphics[width=\textwidth, height=15cm]{Figures/New_Project.png} -->
<!-- \caption{New Project Window} -->
<!-- \end{figure} -->
<!-- \end{frame} -->



# References

https://support.rstudio.com/hc/en-us/articles/200526207-Using-Projects

